---
title: "HW2"
author: "muwuxu"
date: '2022-09-28'
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Q1

```{r}
require(ISLR2)
require(caret)
require(tidyverse)
```

```{r}
# Structure of the Data
data('College')
str(College)
set.seed(1)
```

```{r}
dim(College) # 777 * 18 
summary(College)
# there is no NAs.  
```

```{r}

# split the data
inTrain <- createDataPartition(College$Apps, p = 0.80, list = FALSE)

training <- College[inTrain,]
testing <- College[-inTrain,]

head(training)
nrow(training)

head(testing)
nrow(testing)
```

```{r}
# do the transfomation 
preObj <- preProcess(training, method = c('center', 'scale'))

training <- predict(preObj, training)
testing <- predict(preObj, testing)

head(training)

head(testing)
```

```{r}
# 
y_train <- training$Apps
y_test <- testing$Apps

# change the categorical to dummy 
one_hot_encoding <- dummyVars(Apps ~ ., data = training)
x_train <- predict(one_hot_encoding, training)
x_test <- predict(one_hot_encoding, testing)

dim(x_train)
colnames(College)
colnames(x_train)
head(x_train)

```

```{r}
lin_mod <- lm(Apps ~ ., data = training)

pred <- predict(lin_mod, testing)

lin_info <- postResample(pred, testing$Apps)
lin_info
```

```{r}
ridge_mod <- train(x = x_train, y = y_train,
                   method = 'glmnet', 
                   trControl = trainControl(method = 'cv', number = 10),
                   tuneGrid = expand.grid(alpha = 0,
                                          lambda = seq(0, 10e3, length.out = 20)))

ridge_info <- postResample(predict(ridge_mod, x_test), y_test)
ridge_info
```

```{r}
coef(ridge_mod$finalModel, ridge_mod$bestTune$lambda)
```

```{r}
lasso_mod <- train(x = x_train, y = y_train, 
                   method = 'glmnet',
                   trControl = trainControl(method = 'cv', number = 10),
                   tuneGrid = expand.grid(alpha = 1,
                                          lambda = seq(0.0001, 1, length.out = 50)))

lasso_info <- postResample(predict(lasso_mod, x_test), y_test)
lasso_info
```

```{r}
as_data_frame(rbind(lin_info,
      ridge_info,
      lasso_info)) %>%
    mutate(model = c('Linear', 'Ridge', 'Lasso' ))

## The models all perform similarly. R2 around 87% for them all and RMSE≤0.35. When we compare the RMSE scores with the mean and standard deviation of the response variable we see that the models all have great accuracy. So there are not much differences between these three approaches. 
```

# Q2

```{r}
library(ggplot2)
library(caret)
library(glmnet)
library(gridExtra)
library(leaps)
library(pROC)

```

Can you predict who will be interested in buying a caravan insurance policy and give an explanation why? Yes. Becaues we can use the features to fit a model and then predict the probability so to priedict who will be interested in buying the insurance.

```{r}
train_data <- read.delim("./ticdata2000.txt", header = FALSE, sep = "\t", dec = ".")
test_data <-  read.delim("./ticeval2000.txt", header = FALSE, sep = "\t", dec = ".")
targets <-    read.delim("./tictgts2000.txt", header = FALSE, sep = "\t", dec = ".")
names(targets) = "V86"
test_data = cbind(test_data,targets)
head(test_data)
```

## Explore data

```{r}
dim(train_data)
head(train_data)

dim(test_data)
head(test_data)
head(targets)
str(train_data)
```

forward selection

```{r}
# Formula for scope

regfit.fwd <- regsubsets(V86~., data = train_data, nbest = 1, nvmax = ncol(train_data), method = "forward")
my_sum_fwd <- summary(regfit.fwd)
my_sum_fwd$outmat

par(mfrow = c(2, 2))
plot(my_sum_fwd$cp,xlab = "Num of Variables", ylab = "Cp", type = "l", main = paste("Min Error at",which.min(my_sum_fwd$cp), "Variables"))
points(which.min(my_sum_fwd$cp), my_sum_fwd$cp[which.min(my_sum_fwd$cp)], col = "steelblue", cex = 2, pch = 20)

plot(my_sum_fwd$bic,xlab = "Num of Variables", ylab = "BIC", type = "l", main = paste("Min Error at",which.min(my_sum_fwd$bic), "Variables" ))
points(which.min(my_sum_fwd$bic), my_sum_fwd$bic[which.min(my_sum_fwd$bic)], col = "darkgoldenrod", cex = 2, pch = 20)

plot(my_sum_fwd$adjr2,xlab = "Num of Variables", ylab = "Adjusted_R^2", type = "l", main = paste("Max AdjR2",which.max(my_sum_fwd$adjr2), "Variables"))
points(which.max(my_sum_fwd$adjr2), my_sum_fwd$adjr2[which.max(my_sum_fwd$adjr2)], col = "magenta", cex = 2, pch = 20)

plot(my_sum_fwd$rss,xlab = "Num of Variables", ylab = "Residual Sum of Squares", type = "l", main = paste("Min Error at",which.min(my_sum_fwd$rss), "Variables"))
points(which.min(my_sum_fwd$rss), my_sum_fwd$rss[which.min(my_sum_fwd$rss)], col = "cyan", cex = 2, pch = 20)
```

```{r}
## using adj R2 as the metrics to select variables
length(rownames(data.frame(coef(regfit.fwd,47)))[-1])
paste(rownames(data.frame(coef(regfit.fwd,47)))[-1], collapse = "+")
```

```{r}
glm_fwd <- glm(V86 ~ V2+V4+V6+V7+V8+V10+V14+V16+V18+V21+V22+V23+V28+V30+V31+V32+V33+V34+V35+V36+V39+V41+V42+V43+V44+V46+V47+V50+V51+V53+V55+V57+V58+V59+V60+V61+V65+V72+V73+V76+V78+V79+V80+V81+V82+V83+V85, 
    data= train_data, 
    family = binomial(link = "logit"))
summary(glm_fwd)

y_hat_test = predict(glm_fwd, test_data, type = 'response')
summary(y_hat_test)
r4 <- roc(as.vector(targets$V86), as.vector(y_hat_test))
p = coords(r4,"best",ret="ppv")
predicted.classes <- ifelse(y_hat_test > p[1,1], 1, 0)
table(predicted.classes)
mean(predicted.classes == targets)
confusionMatrix(table(predicted.classes, targets[,1]), positive = "1")
```

backward selection

```{r }
regfit.bwd <- regsubsets(V86~., data = train_data, nbest = 1, nvmax = ncol(train_data), method = "backward")
my_sum_bwd <- summary(regfit.bwd)
my_sum_bwd$outmat

par(mfrow = c(2, 2))
plot(my_sum_bwd$cp,xlab = "Num of Variables", ylab = "Cp", type = "l", main = paste("Min Error at",which.min(my_sum_bwd$cp), "Variables"))
points(which.min(my_sum_bwd$cp), my_sum_bwd$cp[which.min(my_sum_bwd$cp)], col = "steelblue", cex = 2, pch = 20)

plot(my_sum_bwd$bic,xlab = "Num of Variables", ylab = "BIC", type = "l", main = paste("Min Error at",which.min(my_sum_bwd$bic), "Variables" ))
points(which.min(my_sum_bwd$bic), my_sum_bwd$bic[which.min(my_sum_bwd$bic)], col = "darkgoldenrod", cex = 2, pch = 20)

plot(my_sum_bwd$adjr2,xlab = "Num of Variables", ylab = "Adjusted_R^2", type = "l", main = paste("Max AdjR2",which.max(my_sum_bwd$adjr2), "Variables"))
points(which.max(my_sum_bwd$adjr2), my_sum_bwd$adjr2[which.max(my_sum_bwd$adjr2)], col = "magenta", cex = 2, pch = 20)

plot(my_sum_bwd$rss,xlab = "Num of Variables", ylab = "Residual Sum of Squares", type = "l", main = paste("Min Error at",which.min(my_sum_bwd$rss), "Variables"))
points(which.min(my_sum_bwd$rss), my_sum_bwd$rss[which.min(my_sum_bwd$rss)], col = "cyan", cex = 2, pch = 20)
```

```{r}
## using adj R2 as the metrics to select variables
length(rownames(data.frame(coef(regfit.bwd,39)))[-1])
paste(rownames(data.frame(coef(regfit.bwd,39)))[-1], collapse = "+")
```

```{r}

glm_bwd <- glm(V86 ~ V1+V2+V4+V5+V6+V9+V10+V14+V17+V18+V21+V22+V28+V30+V35+V36+V41+V42+V43+V44+V46+V47+V55+V57+V58+V59+V60+V63+V65+V69+V76+V78+V79+V80+V81+V82+V83+V84+V85,
    data= train_data, 
    family = binomial(link = "logit"))
summary(glm_bwd)

y_hat_test = predict(glm_bwd, test_data, type = 'response')
summary(y_hat_test)
r4 <- roc(as.vector(targets$V86), as.vector(y_hat_test))
p = coords(r4,"best",ret="ppv")
predicted.classes <- ifelse(y_hat_test > p[1,1], 1, 0)
table(predicted.classes)
mean(predicted.classes == targets)
confusionMatrix(table(predicted.classes, targets[,1]), positive = "1")
```

lasso

```{r Lasso}
train_x <- model.matrix(V86 ~ . , data = train_data)[, -1]
train_y <- train_data$V86

set.seed(1234)

cv.lasso <- cv.glmnet(train_x, train_y, alpha = 1, family = "binomial")
plot(cv.lasso)
```

```{r}
lasso_min_lambda <- cv.lasso$lambda.min
# coef(cv.lasso_3, cv.lasso_3$lambda.min)
lasso_min_lambda
```

```{r}
lasso_model <- glmnet(train_x, train_y, alpha = 1, family = "binomial", lambda = lasso_min_lambda)
coef(lasso_model)[,1]
```

# lasso will penalize the coefficient to 0

```{r}
lasso_coef <- data.frame("coef" = coef(lasso_model)[,1])
lasso_var <- paste(rownames(lasso_coef[lasso_coef$coef != 0, , drop=F][-1, ,drop=F]) , collapse = "+", sep = "")
lasso_var
```

```{r}
glm_lasso <- glm(V86 ~ V4+V7+V9+V10+V11+V16+V18+V21+V22+V30+V32+V37+V40+V41+V42+V43+V44+V46+V47+V57+V58+V59+V62+V73+V81+V82+V83+V85
                   , data = train_data, 
                   family = binomial(link = "logit"))
glm_lasso_sum <- summary(glm_lasso)
glm_lasso_sum

y_hat_test = predict(glm_lasso, test_data, type = 'response')
summary(y_hat_test)
r4 <- roc(as.vector(targets$V86), as.vector(y_hat_test))
p = coords(r4,"best",ret="ppv")
predicted.classes <- ifelse(y_hat_test > p[1,1], 1, 0)
table(predicted.classes)
mean(predicted.classes == targets)
confusionMatrix(table(predicted.classes, targets[,1]), positive = "1")
```

Ridge Regression

```{r Ridge Regression}
set.seed(1234)

cv.ridge <- cv.glmnet(train_x, train_y, alpha = 0, family = "binomial")

plot(cv.ridge, main = "RIDGE REGRESSION LAMBDAS")
```

We choose the optimal value of lambda for Regressing which is one standard error away from the maximum AUC.

```{r Plot lambda for Ridge regression}
ridge_min_lambda <- cv.ridge$lambda.min
ridge_min_lambda
```

```{r Coefficients of Ridge regression}
ridge_model <- glmnet(train_x, train_y, alpha = 0, family = "binomial", lambda = ridge_min_lambda)
coefficients(ridge_model)[,1]
```

ridge regression don't panel the coefficient to 0

```{r}
y_hat_test <- predict(ridge_model ,newx = as.matrix(test_data[1:85]), type = "response")
summary(y_hat_test)
r4 <- roc(as.vector(targets$V86), as.vector(y_hat_test))
p = coords(r4,"best",ret="ppv")
predicted.classes <- ifelse(y_hat_test > p[1,1], 1, 0)
table(predicted.classes)
mean(predicted.classes == targets)
confusionMatrix(table(predicted.classes, targets[,1]), positive = "1")
```

### forward:

               Accuracy : 0.877          
            Sensitivity : 0.3277         
            Specificity : 0.9117         
         Pos Pred Value : 0.1902         
         Neg Pred Value : 0.9554    
         

### backward:

               Accuracy : 0.8702          
            Sensitivity : 0.3529          
            Specificity : 0.9030          
         Pos Pred Value : 0.1871          
         Neg Pred Value : 0.9566          

### lasso

               Accuracy : 0.8455          
            Sensitivity : 0.37395         
            Specificity : 0.87533         
         Pos Pred Value : 0.15950         
         Neg Pred Value : 0.95671               
         

### ridge:

               Accuracy : 0.8482          
            Sensitivity : 0.3782          
            Specificity : 0.8780          
         Pos Pred Value : 0.1639          
         Neg Pred Value : 0.9571            
         
         

# conclusion

they have a very similar performance however in terms of the best prediction in buying the insurance (PPV) I think the forward selection wins with 0.19. And also forward selection have a better accuracy rate with 0.87.

# Q3

ESL textbook exercise 2.8 modified: Compare the classification performance of linear regression and k-nearest neighbor classification on the zipcode data. In particular, consider only the 7's and 9's for this problem, and k = 1, 3, 5, 7, 9, 11, 13,15. Show the test error for each choice of k. Describe your results -- are you surprised by the differences in performance?

```{r}
# Read in the training data
X <- as.matrix(read.table("zip.train"))
y7or9 <- which(X[, 1] == 7 | X[, 1] == 9)
train_x <- X[y7or9, -1]
train_y <- ifelse(X[y7or9, 1] == 7, 1,0 )

# Read in the test data
X <- as.matrix(read.table("zip.test"))
y7or9 <- which(X[, 1] == 7 | X[, 1] == 9)
test_x <- X[y7or9, -1]
test_y <- ifelse(X[y7or9, 1] == 7, 1,0 )


```

```{r}
# Classification by linear regression
L <- lm(train_y ~ train_x)
summary(L)
# from the result we could see that there are high collinearity and so some of the coefficients are NA. 
# drop the NA term  
L$coefficients[is.na(L$coefficients)]=0
L$coefficients
# Classification by linear regression

yhat <- (cbind(1, test_x) %*% L$coef) >= 0.5
L.error <- mean(yhat != test_y)
L.error
```

```{r}
# Classification by k-nearest neighbors
library(class)
k <- c(1, 3, 5, 7,9,11,13, 15)
k.error <- rep(NA, length(k))
for (i in 1:length(k)) {
    yhat <- knn(train_x, test_x, train_y, k[i])
    k.error[i] <- mean(yhat != test_y)
}
```

```{r}
# Compare results
error <- matrix(c(L.error, k.error), ncol = 1)
colnames(error) <- c("Error Rate")
rownames(error) <- c("Linear Regression", paste("k-NN with k =", k))
error


#                   Error Rate
# Linear Regression 0.04629630
# k-NN with k = 1   0.02469136
# k-NN with k = 3   0.02469136
# k-NN with k = 5   0.02469136
# k-NN with k = 7   0.02777778
# k-NN with k = 9   0.03703704
# k-NN with k = 11  0.04012346
# k-NN with k = 13  0.04012346
# k-NN with k = 15  0.03703704

# the result is not that different and the best kNN result is when k = 1 which is very surprising to me. 

plot(c(1, 15), c(0, 1.1 * max(error)), type = "n", main = "Comparing Classifiers (Linear vs KNN (different K))", 
     ylab = "Error Rate", xlab = "k")
abline(h = L.error, col = 2, lty = 4,  lwd= 3)
points(k, k.error, col = 4)
lines(k, k.error, col = 4, lty = 2)
```
